Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
include plant G_4

The discrete controllers $C_{4}$ and $C_{5}$ for the satellite plant $G_{3}$,discretized with sample time equal to $1 s$ and $2 s$ respectively, 
are represented by the following z-expression:
%
\begin{equation}
\label{satellite-b2}
C_{4}(z)=\frac{2.88z^2 - 4.896z + 2.074}{1.0z^2 - 0.42z - 0.3465 - 0.03915}. \nonumber
\end{equation} 
%
\begin{equation}
\label{satellite-c2}
C_{5}(z)=\frac{0.43z^2 - 0.2408z - 0.1316}{1.0z^2 + 1.5z + 0.97 + 0.183}. \nonumber
\end{equation}

@@

\begin{table}[H]
\centering
\begin{tabular}{c l | r l}
Plant & Benchmark                  & Time    & \\\cline{1-3}
$G_1$ & CruiseControl02            & 17\,s   & \\
$G_1$ & CruiseControl02$^\dagger$  & 46\,s   & \\
$G_2$ & SpringMassDamper           & 28\,s   & \\
$G_2$ & SpringMassDamper$^\dagger$ & \xmark  & \\
$G_3$ & SatelliteB2                & 7\,s    & \\
$G_3$ & SatelliteB2$^\dagger$      & 6601\,s & \tbmark\\
$G_3$ & SatelliteC2                & 2\,s    & \\
$G_3$ & SatelliteC2$^\dagger$      & 76\,s   & \tbmark\\
      & a\_PL1\_SCH2\_IMPL1        & 2704\,s & \\
      & a\_PL1\_SCH2\_IMPL2        & 538\,s  & \\
      & a\_PL1\_SCH2\_IMPL3        & 12\,s   & \\
      & a\_PL1\_SCH3\_IMPL1        & 318\,s  & \\
      & a\_PL1\_SCH3\_IMPL2        & 967\,s  & \\
      & a\_PL1\_SCH3\_IMPL3        & 9798\,s & \\
      & a\_PL1\_SCH4\_IMPL1        & 6304\,s & \\
\end{tabular}

>>>>

The discrete controllers $C_{4}$ and $C_{5}$ for the satellite plant $G_{3}$, discretized with sample time $1s$ and $2s$ respectively, 
are represented by the following z-expression:
%
\begin{equation}
\label{satellite-b2}
C_{4}(z)=\frac{2.88z^2 - 4.896z + 2.074}{1.0z^2 - 0.42z - 0.3465 - 0.03915}. \nonumber
\end{equation} 
%
\begin{equation}
\label{satellite-c2}
C_{5}(z)=\frac{0.43z^2 - 0.2408z - 0.1316}{1.0z^2 + 1.5z + 0.97 + 0.183}. \nonumber
\end{equation}

@@

\begin{table}[H]
\centering
\begin{tabular}{c | l | r l}
Plant & Benchmark                  & Time    & \\\cline{1-3}
$G_1$ & CruiseControl02            & 17\,s   & \\
$G_1$ & CruiseControl02$^\dagger$  & 46\,s   & \\
$G_2$ & SpringMassDamper           & 28\,s   & \\
$G_2$ & SpringMassDamper$^\dagger$ & \xmark  & \\
$G_3$ & SatelliteB2                & 7\,s    & \\
$G_3$ & SatelliteB2$^\dagger$      & 6601\,s & \tbmark\\
$G_3$ & SatelliteC2                & 2\,s    & \\
$G_3$ & SatelliteC2$^\dagger$      & 76\,s   & \tbmark\\
$G_4$ & a\_PL1\_SCH2\_IMPL1        & 2704\,s & \\
$G_4$ & a\_PL1\_SCH2\_IMPL2        & 538\,s  & \\
$G_4$ & a\_PL1\_SCH2\_IMPL3        & 12\,s   & \\
$G_4$ & a\_PL1\_SCH3\_IMPL1        & 318\,s  & \\
$G_4$ & a\_PL1\_SCH3\_IMPL2        & 967\,s  & \\
$G_4$ & a\_PL1\_SCH3\_IMPL3        & 9798\,s & \\
$G_4$ & a\_PL1\_SCH4\_IMPL1        & 6304\,s & \\
\end{tabular}
